GSE158422: DNA methylation in Lung squamous cell carcinoma

### 2023-12-21 figs/GSE158422.Rmd
samplesheet
fixes

tumor <- factor(samplesheet$`tumor:ch1`,levels=c("normal","tumor"))

@@

make_dm_plots(dm = dm ,name=name , mx=beta,mxs=mxs, groups = groups,
  confects=confects,dmr = dmr, comp=comp, cgi=cgi)

>>>>

tumor <- factor(samplesheet$tumor,levels=c("normal","tumor"))

@@

make_dm_plots(dm = dm ,name=name , mx=beta,mxs=mxs, groups = tumor,
  confects=confects,dmr = dmr, comp=comp, cgi=cgi)
